The shape of dark matter halos in the AURIGA simulations

### 2019-07-10 Document/paper.tex

\begin{figure*}
  \includegraphics[width=\columnwidth]{./pics/Redshift/halo_27_DM_Z_correlation.png}
  \includegraphics[width=\columnwidth]{./pics/Redshift/halo_24_level3_MHD_Z_Triax.png}
  \caption{Radial profile at $z=0$ (dashed line) and 
    the historical profile at the virial radius (colour line). 
    Results for DM simulations on the left, for MHD on the right.
    {\bf Aqui la idea es mostrar el mismo
      halo, no halos diferentes!}} 
  \label{fig:redshift_triaxial}
\end{figure*}

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{./pics/Delta asphericity Vs Star Density.png}
  \caption{Difference in asphericities between MHD and DM shapes Vs
    Star Density of the simulation. Unsure about this graphic. Take
    delta asphericity as the strength of the rounding effect of
    baryons.}  
  \label{fig:Star_Density_effect}
\end{figure}

@@

\begin{figure*}
\centering
{\includegraphics[width=0.6\textwidth]{./pics/Shape_Methods/q_pot_Vs_q_den.png}}
\caption{Comparison of q calculated with isopotential and with density enclosed volumes. Continuous lines represent the Binney and Tremaine approximations for different ratios s. Scatter points represent the calculated shapes with an isopotential approximation and with the Allgood method} \label{fig:shape_comp}
\end{figure*}

\begin{figure*}
\centering
{\includegraphics[width=0.6\textwidth]{./pics/Shape_Methods/s_pot_Vs_s_den.png}}
\caption{Comparison of s calculated with isopotential and with density enclosed volumes. Continuous lines represent the Binney \& Tremaine approximation. In the case of the ratio s, it does not depend on q.ds Scatter points represent the calculated shapes with an isopotential approximation and with the Allgood method} \label{fig:shape_comp}
\end{figure*}

>>>>

\begin{figure*}
  \includegraphics[width=\columnwidth]{./pics/Redshift/halo_27_DM_Z_correlation.png}
  \includegraphics[width=\columnwidth]{./pics/Redshift/halo_24_level3_MHD_Z_Triax.png}
  \caption{Radial profile at $z=0$ (dashed line) and 
    the historical profile at the virial radius (colour line). 
    Results for DM simulations on the left, for MHD on the right.{\bf
      Update with halo 24}}
  \label{fig:redshift_triaxial}
\end{figure*}

@@

%\begin{figure}
%  \includegraphics[width=\columnwidth]{./pics/Delta asphericity Vs Star Density.png}
%  \caption{Difference in asphericities between MHD and DM shapes Vs
%    Star Density of the simulation. Unsure about this graphic. Take
%    delta asphericity as the strength of the rounding effect of
%    baryons.}  
%  \label{fig:Star_Density_effect}
%\end{figure}

\begin{figure*}
\centering
\includegraphics[width=0.4\textwidth]{q_pot_vs_q_den.pdf}
\includegraphics[width=0.4\textwidth]{s_pot_vs_s_den.pdf}
\caption{Comparison of $q$ and $s$ calculated with isopotential or
  density enclosed volumes. 
  Continuous lines represent the Binney and Tremaine approximations
  and the dots are the measurements on the simulations.}
\label{fig:shape_comp} 
\end{figure*}

@@
